Linting Linearity in Core/System FC

### 2022-11-17 proposal.tex
Case binder unifying solution

Idea: if $x$ was anotated with some information regarding the CSE then perhaps
it could be typechecked (in a system that considered said anotations)

@@

>>>>

Idea: if $x$ was anotated with some information regarding the CSE then perhaps
it could be typechecked (in a system that considered said anotations) -- This is
too specific and the case binder environment solution is much cleaner. It just
requires that the example is changed into using the case binder $w1$ rather than
$x$.

Solution with the (unifying) case binder idea:
Annotate the case binder with its usage environment. For enums without arguments
this usage environment will always be empty, meaning we can always use the case
binder instead of the actual enum without issues. This solves this problem as
well as a handful of other.

In this exact example, the binder has usage environment empty ($w1 := []$),
meaning that in the False branch, when we use $x$, if we instead used $w1$ which
is equivalent and seems more correct (since it doesn't need the case scrutinee
expression to be a variable), then the usage of $w1$ would imply the usage of
$[]$ which is nothing and therefore we would preserve linearity

@@

Solution with the case binder idea that unifies a different problems:
The case binder is annotated with a usage environment $U_wwj = []$, and its
usage is equal to using the usage environment

Here it would mean that second \textbf{case of} $wwj$ doesn't actually use any
variables and hence it isn't used twice.

\subsection{Artificial examples}

Following the difficulties in consuming or not consuming the case binder and its
associated bound variables linearly we constructed some additional examples that
bring out the problem quite clearly
\begin{code}
case x of w1
    (x1,x2) -> case y:Bool of
                DEFAULT -> (x1,x2)
\end{code}
Is equal to (note that the case binder is being used rather than the $x$ case
scrutinee which could be an arbitrary expression and hence really cannot be
consumed multiple times?)
\begin{code}
case x of w1
    (x1,x2) -> case y:Bool of
                DEFAULT -> w1
\end{code}

We initially wondered whether x was being consumed if the pattern match ignored
some of its variables. We put that if it does have wildcards then it isn't
consuming x fully
\begin{code}
case x of w1
    (_,x2) -> Is x being consumed? no because not all of its components are
    being consumed?
\end{code}

Can we have a solution that even handles weird cases in which we pattern match
twice on the same expression but only on one constructor argument per time?
\begin{code}
case exp of w1
    (x1,_) -> case w1 of w2
                (_, x2) -> (x1, x2)
\end{code}
